*flippant* -- An R package for the automated analysis of dithionite scramblase

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayStats" to "scramblase_assay_stats";

```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
```

@@

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 1C
by `scramblase_assay_plot` in a call to `scramblaseAssayStats`, this is achieved
and produces tabular output represented in Table 1.

```{r, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblaseAssayStats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
```

```{r, echo = FALSE}
ppr_results <- scramblaseAssayStats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblaseAssayStats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    splitByExperiment = FALSE)
  scramblaseAssayStats(
    x,
    generation_of_algorithm = 1, 
    splitByExperiment = FALSE)
}

>>>>

```{r, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
```

@@

The graphical representation of the fit constant $\alpha$ in the PPR plots is
difficult to visually evaluate and easy access to the numeric values desirable.
Recapitulation of the calculations underlying PPR plot generation for Figure 1C
by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved
and produces tabular output represented in Table 1.

```{r, eval = FALSE}
# Write out results in tabular manner (Table 1)
scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
```

```{r, echo = FALSE}
ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
ppr_results_names <- ppr_results$`Experimental Series` %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
  signif(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
```

@@

analysis_timing_function <- function(){
  scramblase_assay_traces(
    x,
    timeMaxSec = 350)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1)
  scramblase_assay_plot(
    x,
    generation_of_algorithm = 1,
    splitByExperiment = FALSE)
  scramblase_assay_stats(
    x,
    generation_of_algorithm = 1, 
    splitByExperiment = FALSE)
}
